### 2013-11-22 research/paper/Theory/mathematical_model.tex
Committing intro after merging versions and minor changes to mathematical_model (title of section)
Committing small changes to th mathematical model and some initial changes to the results section
uploaded 22-11-2013 10.34 pm

\section{Background theory}
\label{sec:theory}

@@

In the QSS model, it is assumed that the force on the body at a given instantaneous angle of attack $\theta$ (defined in figure \ref{fig:setup_1}) is the same as the mean force on a static body at the same angle of attack. The instantaneous value of $C_y$ is therefore determined by an interpolating polynomial based on the lift and drag data  for flow over a stationary body at various $\theta$. Using the relationship between $\theta$ and the instantaneous transverse velocity of the body $\dot{y}$ shown in figure \ref{fig:setup_1}, $C_y$ can be written as a function of $\dot{y}$. The order of the interpolation polynomial used to define this functio has varied from study to study. For  example a $7^{th}$ order polynomial was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}. \cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order doesn't provides a significantly better result. Thus a $7 ^{th}$ order interpolating polynomial is used in this present study. As a result, $C_y(\dot{y})$ is defined as
\begin{equation}
\label{cy ploynomial}
C_y(\theta)=a_1\left(\frac{\dot{y}}{U}\right)+a_3\left(\frac{\dot{y}}{U}\right)^3+a_5\left(\frac{\dot{y}}{U}\right)^5+a_7\left(\frac{\dot{y}}{U}\right)^7.
\end{equation}

@@

The stationary data and the fluid-structure interaction (FSI) data were obtained using a high-order spectral element routine to simulate the two-dimensional laminar flow.  Simulations involving fluid structure interaction (FSI) were used to provide additional validation of the QSS model. The inlet was placed $20D$ while the outlet situated $60D$ away from the centroid of the body. The side boundaries were placed $20D$ away from the centroid of the body where $D$ was kept as unity throughout this study. The Navier--Stokes equations were solved in an accelerated frame of reference attached to the moving body along with the body equation of motion given in equation \ref{equationofmotion}. A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution. The details of the method can be found in \cite{Thompson2006,Thompson1996a}. This code has been very well validated in fluid-structure interaction problems \citep{Leontini2011,Leontini2007a}.

>>>>

\section{Problem formulation and methodology}
\label{sec:theory}

@@

In the QSS model, it is assumed that the force on the body at a given instantaneous angle of attack $\theta$ (defined in figure \ref{fig:setup_1}) is the same as the mean force on a static body at the same angle of attack. The instantaneous value of $C_y$ is therefore determined by an interpolating polynomial based on the lift and drag data  for flow over a stationary body at various $\theta$. Using the relationship between $\theta$ and the instantaneous transverse velocity of the body $\dot{y}$ shown in figure \ref{fig:setup_1}, $C_y$ can be written as a function of $\dot{y}$. The order of the interpolation polynomial used to define this function has varied from study to study. For  example a $7^{th}$ order polynomial was used in \cite{Parkinson1964} and $3^{rd}$ order polynomial was used in \cite{Barrero-Gil2009}. \cite{Ng2005} concluded that using a $7^{th}$ order polynomial is sufficient and a polynomial higher than that of $7^{th}$ order doesn't provides a significantly better result. Thus a $7 ^{th}$ order interpolating polynomial is used in this present study. As a result, $C_y(\dot{y})$ is defined as
\begin{equation}
\label{cy ploynomial}
C_y(\theta)=a_1\left(\frac{\dot{y}}{U}\right)+a_3\left(\frac{\dot{y}}{U}\right)^3+a_5\left(\frac{\dot{y}}{U}\right)^5+a_7\left(\frac{\dot{y}}{U}\right)^7.
\end{equation}

@@

The stationary data and the fluid-structure interaction (FSI) data were obtained using a high-order spectral element routine to simulate the two-dimensional laminar flow.  Simulations involving fluid structure interaction (FSI) were used to provide additional validation of the QSS model. The inlet was placed $20D$ while the outlet situated $60D$ away from the centroid of the body. The side boundaries were placed $20D$ away from the centroid of the body where $D$ was kept as unity throughout this study. The Navier--Stokes equations were solved in an accelerated frame of reference attached to the moving body along with the body equation of motion given in equation \ref{equationofmotion}. A three-step time splitting scheme together with high-order Lagrangian polynomials were used to obtain the solution. The details of the method can be found in \cite{Thompson2006,Thompson1996a}. This code has been very well validated in a variety of fluid-structure interaction problems \citep{Leontini2007a,Griffith2011,Leontini2011,Leontini2013}.

### 2013-11-22 research/paper/introduction/intro-1.0.tex
Committing small changes to th mathematical model and some initial changes to the results section
uploaded 22-11-2013 10.34 pm

The structure of the paper is as follows. Section \ref{sec:theory} presents the modified QSS model, the method for the calculation of power output, and the parameters used. Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\theta$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber cases. For the low \reynoldsnumber case, the results of the QSS model are compared to those of full direct numerical simulations of the fluid-structure interaction problem. Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.}

>>>>

The structure of the paper is as follows. Section \ref{sec:theory} presents the modified QSS model, the method for the calculation of power output, and the parameters used. Section \ref{sec:results} presents the results, first of the fixed body tests at a range of $\theta$, then of the response characteristics predicted by the integration of the QSS model for both the high and low \reynoldsnumber cases. For the low \reynoldsnumber case, the results of the QSS model are compared to those of full direct numerical simulations of

the fluid-structure interaction problem. Finally, section \ref{sec:conc} presents the conclusions that can be drawn from this work.
